---
title: "Initial Data exploration"
author: "Aevar Johannesson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```


```{r,include=FALSE}
# Load packages and libraries
library(ggplot2)
library(tidyverse)
library(gtable)
library(grid)
library(gridExtra)
library(scales)
library(glmnet)
theme_set(theme_bw())
```


```{r}
# Read in the data from Kaggle
data <- read.csv("international_matches.csv")
schedule <- read.csv("matchs-schudule.csv",sep = ";")
Teams <- read.csv("Qatar2022-teams.csv",sep=";")
```


# Information on data


The data includes games from 08-08-1993 to 14-06-2022.

date: Date of the game
home_team: Name of home_team
away_team: Name of away_team
home_team_continent: Continent of home team
away_team_continent: Continent of away team
home_team_fifa_rank: Rank of home team
away_team_fifa_rank: Rank of away team
home_team_total_fifa_points: Total Fifa points for the home team
away_team_total_fifa_points: Total Fifa points for the away team
home_team_score: Goals for the home team
away_team_score: Goals for the away team
tournament: What tournament
city: In what city it was played
country: In what country the game was played
Neutral_location: Neutral location or not?
Shoot_out: Was it a shoot_out or not?
home_team_result: Match result of the home team, including penalty-shootouts

```{r}
# Only look at data after 2010
data <- data %>%
  filter(date >= '2010-01-01')
```


```{r}
# Change the name of Korea and Iran to match the game schedule
data <- data %>%
  mutate(home_team = case_when(
    home_team == 'Korea Republic' ~ 'South Korea',
    home_team == 'IR Iran' ~ 'Iran',
    1 == 1 ~ home_team
  ),
    away_team = case_when(
    away_team == 'Korea Republic' ~ 'South Korea',
    away_team == 'IR Iran' ~ 'Iran',
    1 == 1 ~ away_team
  ))


```






